Visual Interrogation of Attention-Based Models for Natural Language Inference and Machine Comprehension

### 2018-06-01 EMNLP-demo-paper/intro.tex
minor fix

To address these challenges in interpreting attention-based models, 
we introduce a python library that allows users to create web-based interactive visual analytics environments,
in which they can interrogate the model by perturbing the input text and observing the effects on the attention and prediction, or modifying the attention and studying how it affects predictions (see Figure~\ref{fig:modelPipeline}).
%
We demonstrate our system on two primary NLP tasks: natural language
inference (NLI) and machine comprehension (MC). 
%For the NLI task, we visualize
%decomposable attention networks which represents a series of strongly performing models \cite{Parikh2016}.
%For the MC task, we present your visualization methods on bidirectional attention flow model,
%which also represents a line of state-of-the-art models \cite{Seo2016}.

>>>>

To address these challenges in interpreting attention-based models, 
we introduce a Python library that allows users to create web-based interactive visual analytics environments,
in which they can interrogate the model by perturbing the input text and observing the effects on the attention and prediction, or modifying the attention and studying how it affects predictions (see Figure~\ref{fig:modelPipeline}).
%
We demonstrate our system on two primary NLP tasks: natural language
inference (NLI) and machine comprehension (MC). 
%For the NLI task, we visualize
%decomposable attention networks which represents a series of strongly performing models \cite{Parikh2016}.
%For the MC task, we present your visualization methods on bidirectional attention flow model,
%which also represents a line of state-of-the-art models \cite{Seo2016}.
